The symmetric \textit{Fermi} and eROSITA bubbles problem: A proof-of-concept study

### 2022-01-28 paper.tex
update

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__zoom-in-disk.png}
    \caption{Close-up view of the\
             pressure (top), temperature (middle), and number density (bottom) slices\
             in the y-z plane through the center of the disk.
             }
    \label{fig__zoom-in-disk}
  \end{figure}

>>>>

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/fig__zoom-in-disk.png}
    \caption{Close-up view of the initial\
             pressure (top), temperature (middle), and number density (bottom) slices\
             in the y-z plane through the center of the disk.
             }
    \label{fig__zoom-in-disk}
  \end{figure}
